Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Wrote about the assumptions we make when evaluating summaries

\begin{itemize}
  \item arXiv's unique identifier
  \item title
  \item abstract
  \item body of the paper
\end{itemize}

@@

Evaluating a summary is a difficult task because there is no single summary that would be ideal for a given document. In most cases even human evaluators can not agree on which of the given summaries is better.\cite{das-7}. Unlike other NLP problems, like translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad. Manual evaluation of summaries is too expensive, so in the following sections we will only consider automatic techniques.

Automatic evaluation metrics compare manually written ideal summaries with summaries generated automatically by summarization systems.

>>>>

\begin{enumerate}
  \item arXiv's unique identifier
  \item title
  \item abstract
  \item body of the paper
\end{enumerate}

@@

Evaluating a summary is a difficult task because there is no such thing as a single summary that would be ideal for a given document. In most cases even human evaluators can not agree on which of the given summaries is better\cite{das-7}. Unlike other NLP problems, such as translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad. Therefore we must make assumptions about the space of good summaries.

\begin{enumerate}
\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
\end{enumerate}

In the following sections we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).
